%-------------------------
% Resume in Latex
% Author : Harsh Mittal, 2018eeb1150@iitrpr.ac.in
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}

% --- UNIVERSAL PREAMBLE BLOCK (Adapted for pdfLaTeX Compilation) ---
% Using your specific geometry settings
\usepackage[a4paper, left=0.5cm, top=0.5cm, right=0.5cm, bottom=1cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern} % Latin Modern fonts - clean and professional

% Required for lists
\usepackage{enumitem}
\setlist[itemize]{label=-}
% ------------------------------------------------------------------

\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
%\usepackage[empty]{fullpage} % Commented out to respect geometry settings
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
% \usepackage{cfr-lm} % Removed to prevent font conflicts
% \usepackage[T1]{fontenc} % Removed to prevent font conflicts

\usepackage[most]{tcolorbox}
\tcbset{
	frame code={},
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\usepackage[hidelinks]{hyperref}

\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands

\newcommand{\resumeCP}[1]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}
    \end{tabular*}
    \vspace{-1mm}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeAchieve}[2]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\textbf{:}\hspace{0.3mm}#2 
    \end{tabular*}
    \vspace{-1.4mm}
}

\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1},\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Prasanna Nadrajan R} % Your Name
\newcommand{\roll}{241801207} % Your Roll No.
\newcommand{\phone}{8667687297} % Your Phone Number
\newcommand{\emaila}{prasannanadrajan.r@gmail.com} %Email 1
\newcommand{\emailb}{prasaznat@gmail.com} %Email 2
\newcommand{\github}{https://github.com/Prasanna-Nadrajan} %Github
\newcommand{\website}{https://prasazx.tech/} %Website
\newcommand{\linkedin}{https://www.linkedin.com/in/prasannanadrajan}
\newcommand{\college}{Rajalakshmi Engineering College , Chennai}
%linkedin




\begin{document}
% \fontfamily{cmr}\selectfont % Removed as fontspec/Noto Serif handles this now
%----------HEADING-----------------
\parbox{\dimexpr\linewidth\relax}{
\begin{tabularx}{\linewidth}{L r}
  \textbf{\LARGE \name} & +91-\phone\\
  {B.Tech - Artificial Intelligence and Data Science} &  \href{mailto:\emaila}{\emaila}\\
  $|$ \href{\website}{My Portfolio (prasazx.tech)} &  \href{\github}{GitHub} \\
  {\college} &  \href{\linkedin}{LinkedIn}\\
   
\end{tabularx}
}

\vspace{-1mm}

%-----------PROFESSIONAL SUMMARY-----------------
\section{\textbf{Professional Summary}}
\vspace{1mm}
\small{Aspiring AI and Data Science professional with hands-on experience in Machine Learning, Computer Vision, and Data Analytics. Proficient in Python, SQL, and cloud technologies with a proven track record of building impactful projects. Strong problem-solving skills with 100+ coding challenges completed and active participation in hackathons and technical workshops.}
\vspace{1mm}

%-----------EDUCATION-----------------
% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Indian Institute of Technology Guwahati}{Guwahati, India}
%       {Bachelor of Technology in Mathematics and Computing ;  GPA: 8.10}{July. 2015 -- July. 2019 (Expected)}
%     \resumeSubheading
%       {Burdwan Model School}{Burdwan, W.B}
%       {Central Board of Secondary Education (Class XII);  Percentage: 96.60}{March. 2015}
%   \resumeSubHeadingListEnd\vspace{-3mm}
\section{\textbf{Education}}
\vspace{2.5mm}
\setlength{\tabcolsep}{6pt} % Default value: 6pt
% \renewcommand{\arraystretch}{1.1} % Default value: 1
\small{\begin{tabularx}
{\dimexpr\textwidth-2mm\relax}{|c|C|c|c|}
  \hline
  \textbf{Degree } & \textbf{Institute/Board} & \textbf{CGPA/Percentage} & \textbf{Year}\\
  \hline
  Bachelor of Technology & {\college} & 8.87/10 (Current) & 2024-Present\\
  
  %\hline
  %Minor in CSE & Indian Institute of Technology, Ropar & 8.52 %(Till 6th Sem) & 2018-2022\\
 
  \hline
  Senior Secondary & The Hindu Senior Secondary School & 89.60\% & 2024 \\
  \hline
  Secondary & The Hindu Senior Secondary School & 82.67\% & 2022 \\
  \hline
\end{tabularx}}
\vspace{0mm}

%-----------EXPERIENCE-----------------
\section{\textbf{Work Experience}}
  \resumeSubHeadingListStart
\vspace{2.5mm}
    \resumeSubheading
      {Evo Astra Ventures Private Limited}{Remote}
      {Data Science Intern}{Dec 2025 - Jan 2026}
      \vspace{1.5mm}
      \resumeItemListStart
    \item {Developing and implementing data science solutions to drive business insights and decision-making.}
    \item {Analyzing large datasets and building machine learning models for predictive analytics.}
    \item {Collaborating with cross-functional teams to deliver data-driven recommendations.}
    
    \resumeItemListEnd
    \resumeSubheading
      {Indian Space Academy}{Remote}
      {Intern Trainee}{Dec 2025 -  Present}
      \vspace{1.5mm}
      \resumeItemListStart
    \item {Gained hands-on experience in Remote Sensing and GIS technologies, analyzing \textbf{50+ satellite images} for spatial data analysis.}
    \item {Processed and interpreted geospatial datasets covering \textbf{500+ sq km} of terrain for environmental studies.}
    \item {Applied GIS tools including QGIS and ArcGIS to map and interpret spatial patterns with \textbf{95\% accuracy}.}
    
    \resumeItemListEnd
    \resumeSubheading
      {Analyse Research Quant (ARQ)}{Chennai, Tamil Nadu}
      {Data Analyst Associate}{Sep 2025 - Present}
      \vspace{1.5mm}
      \resumeItemListStart
    \item {Led \textbf{hackathons} with \textbf{50+ participants}, applying Python, R, and ML to solve real-world data problems.}
    \item {Built \textbf{3 predictive models} achieving \textbf{85\%+ accuracy} and \textbf{2 interactive dashboards} for data-driven decision making.}
    \item {Organized \textbf{technical workshops} for \textbf{100+ peers}, simplifying complex data science and ML concepts.}
    
    \resumeItemListEnd
    
    % \vspace{-1mm}
    % \resumeSubheading
    %   {Company Name}{Location}
    %   {Position}{June 2021 - July 2021}
    %   \resumeItemListStart
    % \item {About work}
    % \item {About Work}
    
    
    % \item {More work done } .
  \resumeSubHeadingListEnd
\vspace{-4.5mm}

% \section{\textbf{Technical Skills}}
% \vspace{1mm}
% \resumeSubHeadingListStart
% \resumeCP
%     {Competitive Programming:}
% \resumeItemListStart
%     \begin{enumerate}
%         \item {\textbf{CodeChef:} \textbf{5*Star} rated coder with \textbf{2003}(Max) rating points. \href{https://www.codechef.com/users/shivam_4498}{[handle \textbf{shivam\_4498}]}}
%         \item {\textbf{CodeForces:} \textbf{Expert} with the rating of \textbf{1726}(Max). \href{https://codeforces.com/profile/shivu_8944}{[handle \textbf{shivu\_8944}]}}
%     \end{enumerate}
% \resumeItemListEnd
% \resumeSubHeadingListEnd
%     \vspace{-10mm}
%  \resumeHeadingSkillStart
% %   \resumeSubItem{Competitive Programming} {}
% %   \resumeSubItem{\hspace{1mm} 1). CodeChef} 
% %   { \textbf{5*Star} rated coder with \textbf{2003}(Max) rating points. \href{https://www.codechef.com/users/shivam_4498}{[handle \textbf{shivam\_4498}]}}
   
   
% %   \resumeSubItem{\hspace{1mm} 2). CodeForces} 
% %   {\textbf{ Expert} with the rating of \textbf{1726}(Max). \href{https://codeforces.com/profile/shivu_8944}{[handle \textbf{shivu_8944}]} }
  
    
 
%   \resumeSubItem{Programming Languages} % Category
%     { C/C++, Python, SQL}
    
%     %\vspace{-0.5mm}
    
%  \resumeSubItem{Software/Tools/libraries} % Category
%     {Visual Studio, Git, Jupyter, Google Colab} % Skills
% \resumeHeadingSkillEnd
    
%     \vspace{-2mm}

    %\vspace{-0.5mm}
    
%  \resumeSubItem{Skills 3} % Category
%     {blah, blah } % Skills

% %-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{2.5mm}
\resumeSubHeadingListStart

    \resumeProject
      {AI-DRIVEN LAND USE AND LAND COVER CLASSIFICATION (Working)} %Project Name
      {Intern Project} %Project Name, Location Name
      {Jan 2026} %Event Dates
      {\href{https://github.com/Prasanna-Nadrajan/AI-Driven-Land-Use-and-Land-Cover-Classification-}{\textbf{Github}}} %Website
      \resumeItemListStart
        \item {Developed an AI-based LULC mapping system using supervised ML algorithms (Random Forest, SVM) on Sentinel-2 and Landsat-8 multispectral satellite imagery.}
        \item {Implemented geospatial analysis workflows in QGIS and Google Earth Engine for classification, achieving accurate land cover mapping with post-classification refinement.}
    \resumeItemListEnd
    
     \vspace{-1mm}
    \resumeProject
      {AMBULANCE DETECTING TRAFFIC SYSTEM} %Project Name
      {Self Guided Project} %Project Name, Location Name
      {Sep 2025} %Event Dates
      {\href{https://github.com/Prasanna-Nadrajan/Ambulance_detecting_traffic_system}{\textbf{Github}}} %Website
      \resumeItemListStart
        \item {Developed a Smart Traffic Management System using Computer Vision to detect emergency vehicles in real-time through visual and audio cues.}
        \item {Implemented virtual environment with automated traffic light control}
    \resumeItemListEnd
    
     \vspace{-1mm}
    \resumeProject
      {ISLAND RESCUE MISSION} %Project Name
      {DataXscape Hackathon Project} %Project Name, Location Name
      {Jan 2026} %Event Dates
      {\href{https://github.com/Prasanna-Nadrajan/Island-Rescue-Mission}{\textbf{Github}}} %Website
      \resumeItemListStart
        \item {Developed a Power BI dashboard for crisis management simulation, processing SOS signals and environmental data to coordinate rescue operations.}
        \item {Implemented geospatial mapping, DAX measures for distance calculations, and interactive visualizations using Python and ML for data analysis.}
    \resumeItemListEnd
    
     \vspace{-1mm}
    \resumeProject
      {eDNA-VAI-PIPELINE} %Project Name
      {Smart India Hackathon Project} %Project Name, Location Name
      {Sep 2025} %Event Dates
      {\href{https://github.com/Prasanna-Nadrajan/eDNA-VAI-Pipeline}{\textbf{Github}} | \href{https://edna-biodiversity-pipeline-production.up.railway.app/}{\textbf{Live}}} %Website
      \resumeItemListStart
        \item {Engineered an AI pipeline for deep-sea biodiversity assessment using Variational Autoencoder (VAE) to cluster and analyze environmental DNA sequences.}
        \item {Enabled computational discovery and classification of novel taxa and biodiversity patterns from oceanic samples.}
    \resumeItemListEnd
    \vspace{-1mm}
    \resumeProject
      {PROFESSIONAL PORTFOLIO} %Project Name
      {Self Guided Project} %Project Name, Location Name
      {Oct 2025} %Event Dates
      {\href{https://github.com/Prasanna-Nadrajan/Portfolio-Prasaz}{\textbf{Github}} | \href{https://prasazx.tech/}{\textbf{Live}}}
      \resumeItemListStart
        \item {Built a modern, responsive developer portfolio website using TypeScript and React with dynamic animations.}
        \item {Implemented dark/light theme, interactive UI components, and optimized for SEO and performance.}
    \resumeItemListEnd
    
     \vspace{-1mm}
     
      \resumeProject
      {OTHER PROJECTS} %Project Name
      {Self Guided Projects} %Project Name, Location Name
      {Sep 2024 - Present} %Event Dates
      {}
      \resumeItemListStart
      % \vspace{1.5mm}
        % \vspace{0.5mm}
        \item {\textbf{StreamVerse - OTT WebApp, } A modern, responsive OTT streaming platform built with React and Vite, featuring authentication flow, TMDb API integration, watchlist with local storage persistence. \href{https://github.com/Prasanna-Nadrajan/Code-Sapiens-Mentorship-Marathon-2025}{\textbf{[Github]}} | \href{https://streamverse-lemon.vercel.app/}{\textbf{[Live]}}}
        % \vspace{1mm}
        \vspace{5mm}
        \item {\textbf{AI-powered Code Review for ML Pipelines, } Automated code review tool for ML pipelines analyzing best practices and performance bottlenecks. \href{https://github.com/Prasanna-Nadrajan/AI-powered-code-review-for-ML-pipelines}{\textbf{[Github]}}}
        \vspace{5mm}
        \item {\textbf{Loan Eligibility Detector, } Streamlit application predicting loan eligibility using financial and personal data using Random Forest (Machine Learning model). \href{https://github.com/Prasanna-Nadrajan/Loan-Eligibility-Detector}{\textbf{[Github]}}}
        \vspace{5mm}
        % \vspace{0.5mm}
        \item {\textbf{Retail Management System, } Full-stack RMS with FastAPI backend, MySQL database, and vanilla JS frontend featuring POS interface, inventory management, and real-time reporting. \href{https://github.com/Prasanna-Nadrajan/Retail-Management-System}{\textbf{[Github]}}}
        \vspace{5mm}
        \item {\textbf{Zenith - Event Management System, } Full-stack event management application built with Java 17, Spring Boot backend, MySQL database, and HTML5/CSS3/JavaScript frontend. \href{https://github.com/Prasanna-Nadrajan/Zenith}{\textbf{[Github]}}}
        \vspace{5mm}
        \item {\textbf{Billing Management System, } CGI-based system with payment processing, customer management, and history tracking. \href{https://github.com/Prasanna-Nadrajan/Billing_Management_System_Using_C}{\textbf{[Github]}}}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-7mm}

% \section{\textbf{Technical Skills}}
% \vspace{2.5mm}
%  \resumeHeadingSkillStart
%   \resumeSubItem{Competitive Programming} % Category
  
    
 
%   \resumeSubItem{Programming Languages} % Category
%     { C/C++, Python, SQL}
    
%     %\vspace{-0.5mm}
    
%  \resumeSubItem{Software/Tools/libraries} % Category
%     {Visual Studio, Git, Jupyter, Google Colab} % Skills
    
%     %\vspace{-0.5mm}
    
% %  \resumeSubItem{Skills 3} % Category
% %     {blah, blah } % Skills
    
%     %\vspace{-0.5mm}
    
 
%  \resumeHeadingSkillEnd

% \vspace{-1mm}
\section{\textbf{Technical Skills}}
\vspace{1mm}
\resumeSubHeadingListStart
\resumeCP
    {Competitive Programming:}
\resumeItemListStart
    \begin{enumerate}
        \item {\textbf{HackerRank:} \textbf{5-Star} rated coder in Python, C, Java, SQL, and Problem Solving. \href{https://www.hackerrank.com/profile/prasannanadraj07}{\textbf{[prasannanadraj07]}}}
        \item {\textbf{LeetCode:} Solved \textbf{100+ problems} focusing on Data Structures and Algorithms. \href{https://leetcode.com/u/Prasanna_Nadrajan}{\textbf{[Prasanna\_Nadrajan]}}}
        \vspace{2mm}
    \end{enumerate}
\resumeItemListEnd
\resumeSubHeadingListEnd
    \vspace{-10mm}
 \resumeHeadingSkillStart
%   \resumeSubItem{Competitive Programming} {}
%   \resumeSubItem{\hspace{1mm} 1). CodeChef} 
%   { \textbf{5*Star} rated coder with \textbf{2003}(Max) rating points. \href{https://www.codechef.com/users/shivam_4498}{[handle \textbf{shivam\_4498}]}}
   
   
%   \resumeSubItem{\hspace{1mm} 2). CodeForces} 
%   {\textbf{ Expert} with the rating of \textbf{1726}(Max). \href{https://codeforces.com/profile/shivu_8944}{[handle \textbf{shivu\_8944}]} }
  
    
 \vspace{1.5mm}
 \vspace{1.5mm}
  \resumeSubItem{Programming Languages} % Category
    {Python, C, Java, R, JavaScript}
  \resumeSubItem{Machine Learning}
    {Supervised/Unsupervised Learning, Neural Networks, Deep Learning, NLP, Computer Vision, Model Evaluation}
  \resumeSubItem{DataBases}% Category
    {MySQL, MongoDB}
    %\vspace{-0.5mm}
  \resumeSubItem{Data Science Libraries}
    {Pandas, NumPy, Scikit-learn, TensorFlow, Keras, OpenCV, SciPy}
  \resumeSubItem{Software/Tools} % Category
    {Visual Studio Code, Git, GitHub, Jupyter Notebook, Google Colab, Docker} % Skills
  \resumeSubItem{Data Visualization and BI tools}
    {Matplotlib, Seaborn, Plotly, Power BI}
  \resumeSubItem{Web Development (MERN Stack)}
    {MongoDB, Express.js, React, Node.js}
  \resumeSubItem{Cloud Platforms}
    {AWS (Basic)}
  \resumeSubItem{Soft Skills}
    {Communication, Leadership, Teamwork, Creativity, Accountability}
\resumeHeadingSkillEnd
    
    \vspace{-2mm}

    %\vspace{-0.5mm}
    
%  \resumeSubItem{Skills 3} % Category
%     {blah, blah } % Skills

%-----------PROJECTS-----------------
\section{\textbf{Key courses taken}}
\vspace{2.5mm}
\resumeHeadingSkillStart
 \resumeSubItem{ComputerScience Courses} % Category
    { Data Structure \& Algorithm , Object Oriented Programming , DBMS, Java}
    %\vspace{-0.5mm}
\resumeSubItem{DataScience Courses}
 { Machine Learning , Data Analytics}
%  \resumeSubItem{Electrical and Electronics} % Category
%     {Advanced Control Systems, Digital Systems, Microprocessors} % Skills
 \resumeHeadingSkillEnd

\vspace{-1.5mm}

% \section{\textbf{Positions of Responsibility}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Secretary} % Position
%     {XYZ Club, IIT Ropar} %Club,Event
%     {Apr. 2018 - Apr. 2019} %Tenure Period
% \resumePOR{Secretary} % Position
%     {XYZ Club, IIT Ropar} %Club,Event
%     {Apr. 2018 - Apr. 2019} %Tenure Period
% \resumeSubHeadingListEnd
% \vspace{-4mm}


\section{\textbf{Miscellaneous}}
\vspace{2mm}
\resumeSubHeadingListStart
% \resumePOR{CodeChef} % Award
%     { \textbf{5*Star} rated coder with \textbf{2003}(Max) rating points. \href{https://www.codechef.com/users/shivam_4498}{[handle \textbf{shivam\_4498}]}} % Event
%     {2021} %Event Year
% \vspace{-0.1mm}
% \resumePOR{CodeForces} % Award
%     {\textbf{ Expert} with the rating of \textbf{1726}(Max). \href{https://codeforces.com/profile/shivu_8944}{[handle \textbf{shivu\_8944}]} } % Event
%     {2021} %Event Year
% \vspace{-0.1mm}
    \resumePOR{Board Member in Ethics Club REC} % Award
        {Promote ethical practices and awareness within the college community} % Event
        {2025} %Event Year
    \vspace{-0.1mm}
    \resumePOR
        {Completed 100+ days of Coding Challenge}            
        {currently progressing through a 200-day DSA roadmap.}
        {2025}
    \resumePOR{CodeSapiens Git-in-Kadhai} % Award
        { Secured \textbf{3rd position}, among many participants.} % Event
        {2025} %Event Year
    \vspace{-0.1mm}
    \resumePOR{Volunteer}{CII Connect 2024, a big tech meetup in Tamil Nadu}{2024}
    
    \vspace{-0.1mm}

% \vspace{-1.2mm}
\resumeSubHeadingListEnd
\vspace{-2mm}

%-----------LANGUAGES-----------------
\section{\textbf{Languages}}
\vspace{1mm}
\small{\textbf{English} (Fluent) $\bullet$ \textbf{Tamil} (Native) }
\vspace{2mm}

% \hspace*{-5mm}\rule{1.035\textwidth}{0.1mm}


%-------------------------------------------
\end{document}